---
title: "Complaints Final"
author: "Yuhan Wu"
date: "6/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
```


```


```{r get-data, include=FALSE}
raw_data <- read_csv("https://raw.githubusercontent.com/Financial-Times/police-misconduct-complaints-analysis/main/output/philly_clean.csv") %>% 
  select(officer_id, po_race, po_sex)
```

```{r, clean_data}
 clean_data <- raw_data %>% 
  group_by(officer_id) %>% 
  summarise(total = n()) %>% 
  mutate(compl_desc= ntile(total,10))%>%
  group_by(compl_desc)%>%
  arrange(desc(total)) %>% 
  mutate(officer_id = as.character(officer_id)) 
```


```{r, plot_data}
clean_data %>% 
  ggplot(aes(x = officer_id, y = total)) +
    geom_col() +
    labs(title = "Complaints about Police Officers in Philadelphia",
         subtitle = "Most complained about officers have many more complaints than\nthe typical officer",
         x = "Officer",
         y = "Complaints",
         caption = "Data from Financial Times") +
        ntile(data)
         
```

```{r}

```



